### 2024-05-18 content/chapter_2.tex
:triangular_flag_on_post: Minor amendment 240518

		\begin{figure}[H]
			\centering
			\subfloat[Negative-index material\label{fg:nim_focus}]{
				\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/nim_focus.tex}
				}
			}
			\subfloat[Positive-index material\label{fg:pim_diverge}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/chapter_2/pim_diverge.tex}
				}
			}
			\caption{Refraction through metamaterials. For negative-index material, beams diverging from a point source is set in reverse and converges back to another point behind the material.}
		\end{figure}
		\begin{figure}[H]
			\centering
			\subfloat[Incident wave\label{fg:wave_incident}]{
				\resizebox{!}{4.04cm}{
					\input{assets/chapter_2/wave_incident.tex}
				}
			}
			\subfloat[Reflected wave\label{fg:wave_reflected}]{
				\resizebox{!}{4cm}{
					\input{assets/chapter_2/wave_reflected.tex}
				}
			}
			\caption{Reflection through metamaterials. Yellow dots represent scattering elements. Solid and dashed lines denote wavefronts and rays, respectively. The scattering elements work together to manipulate the phases of incident waves, resulting in a focused beam steered in the intended direction.}
		\end{figure}
		It is worth noticing that refraction and reflection are different implementations of \emph{passive beamforming} where the phase and amplitude of the ambient signal are altered by the metamaterial for a desired net effect.
		In the next subsection, we will some typical \gls{ris} scattering models and their physical architecture.
	\end{subsection}

	\begin{subsection}{Wave Scattering Models}
		\begin{subsubsection}{Principles}\label{sc:principles}
			\gls{rf} wave can be manipulated by scattering elements made from \emph{programmable metamaterials} or \emph{passive antennas} \cite{Liang2022}.
			As discussed above, the former refracts or reflects the incident signals at the air-cell boundary and mainly applies a phase shift.
			In contrast, the latter allows the wave to feed into the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
			An interesting observation is that when excited by an external wave, a scattering element can simultaneously function as an object and a radiator.
			The corresponding scattered field is \cite{Hansen1989}
			\begin{equation}
				\vec{E}_\text{scatter}(Z_\mathrm{L}) = \underbrace{\vec{E}_\text{structural}}_\text{structural component} + \underbrace{\Gamma I_\mathrm{M} \vec{E}_\text{antenna}}_\text{antenna component},
			\end{equation}
			where $Z_\mathrm{L}$ is the load impedance, $\vec{E}_\text{structural}$ is the residual field under perfect matching (i.e., modelling as an object), $\vec{E}_\text{antenna}$ is the radiated field with unit current at the terminal and no external excitation (i.e., modelling as a radiator), $I_\mathrm{M}$ is the current under perfect matching, and $\Gamma$ is the reflection coefficient
			\begin{equation}
				\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0},
				\label{eq:reflection_coefficient}
			\end{equation}
			and $Z_0$ is the characteristic impedance for programmable metamaterials or the input impedance for passive antennas.
			Specifically,
			\begin{itemize}
				\item \emph{Structural component:} Depends on the geometry and material of the scatterer. It is usually modelled as part of the environment multipath \cite{Thomas2012,Liang2020} or a baseband \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
				\item \emph{Antenna component:} Depends on the reflection coefficient and load impedance. This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2024}.
			\end{itemize}
			We then introduce two canonical \gls{ris} models that will be adopted in the work chapters.
			Advanced models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and parametric fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature for accurate and practical analysis.
			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
		\end{subsubsection}

@@

		\begin{subsubsection}{\glsfmtfull{bd} Model}
			How to model the \gls{ris} response if the passive scattering elements can cooperate with neighbors via physical connections?
			This question has been answered by \cite{Shen2020a} through a \gls{bd} model.
			From a network theory perspective \cite{Ivrlac2010}, a general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
			It allows wave impinging on any element to propagate within the circuit and depart partially from other elements in the same group, such that both amplitude and phase of the scattered wave can be redistributed with zero power loss.
			Fig. \ref{fg:bd_ris_architecture_2} illustrates an 8-element \gls{ris} with group size 2 (left) and 4 (right).
			\begin{figure}[H]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\includegraphics{assets/chapter_2/bd_ris_architecture_2.eps}
				}
				\caption{Network model of an 8-element \gls{ris} with group-wise cooperative scattering of group size (a) 2 and (b) 4. The group size is a design parameter to balance the circuit complexity and scattering performance. Source: Modified from \cite{Shen2020a}.}
				\label{fg:bd_ris_architecture_2}
			\end{figure}

			% thus redistribute both amplitude and phase of the scattered wave with zero power loss.
			% \begin{figure}[H]
			% 	\centering
			% 	\resizebox{0.75\columnwidth}{!}{
			% 		\includegraphics{assets/chapter_2/bd_ris_architecture_1.eps}
			% 	}
			% 	\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. Source: Modified from \cite{Shen2020a}.}
			% 	\label{fg:bd_ris_architecture_1}
			% \end{figure}

			% A general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
			With symmetric components (e.g., capacitors and inductors), the scattering matrix of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$ is \cite{Shen2020a}
			\begin{equation}
				\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I}),
			\end{equation}
			which satisfies both \emph{symmetric} and \emph{unitary} properties
			\begin{subequations}
				\begin{equation}
					\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T},
					\label{eq:symmetric_property}
				\end{equation}
				\begin{equation}
					\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}.
					\label{eq:unitary_property}
				\end{equation}
			\end{subequations}
			On the other hand, lossless networks may also be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids) \cite{Ahn2006} such that the symmetric constraint \eqref{eq:symmetric_property} is unnecessary.
			This corresponds to the ultimate passive model where energy conservation \eqref{eq:unitary_property} is the only constraint for each group, as has been widely adopted in quantum physics.
			The overall scattering matrix of asymmetric \gls{bd}-\gls{ris} is thus \emph{block-diagonal with unitary diagonal blocks}
			\begin{equation}
				\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G) =
				\begin{bmatrix}
					\mathbf{\Theta}_1 & \mathbf{0} & \cdots & \mathbf{0} \\
					\mathbf{0} & \mathbf{\Theta}_2 & \cdots & \mathbf{0} \\
					\vdots & \vdots & \ddots & \vdots \\
					\mathbf{0} & \mathbf{0} & \cdots & \mathbf{\Theta}_G
				\end{bmatrix},
				\label{eq:bd_scattering_matrix}
			\end{equation}
			where \eqref{eq:unitary_property} is equivalently denoted as $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$.
			The group size $L$ is a design parameter to balance the circuit complexity and scattering performance.
			Diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be viewed as extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
			Therefore, the \gls{bd} model \eqref{eq:bd_scattering_matrix} is envisioned to be the next-generation theoretical foundation for passive \gls{ris}, which grants more design freedom and stronger signal processing capability.

			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2024}.
			Two elements are in the same group if and only if there is at least one path (via edges) between them.
			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
			Antenna directivity and radiation pattern should also be modelled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
		\end{subsubsection}
	\end{subsection}
\end{section}

@@

		The block diagram a closed-loop \gls{ris}-aided \gls{wpt} system is illustrated in Fig. \ref{fg:wpt_architecture}.
		The \gls{rf} signal is generated and radiated by the energy transmitter, propagated through a wireless channel in the presence of a \gls{ris}, captured by the antenna(s) at the receiver, converted to \gls{dc} power by rectifier(s), then passed to the power management unit.
		Upon successful harvesting, the \gls{dc} power is either delivered directly to the device or stored in a battery/super capacitor for future operations.
		When a feedback link is available, one can acquire \gls{csi} at the energy transmitter and exploit it for signal optimization.
		Such a closed-loop \gls{ris}-aided \gls{wpt} system can provide a complete control of transmitter, channel, and receiver, which is essential for maximizing the end-to-end power transfer efficiency
		\begin{equation}
			\eta = \frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{T}} = \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{T}}{P_{\mathrm{DC}}^\mathrm{T}}}_{\eta_1} \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{T}}}_{\eta_2} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{R}}}_{\eta_3} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{R}}}_{\eta_4},
		\end{equation}
		where $P_{\mathrm{DC}}^\mathrm{T}$ is the transmitted \gls{dc} power, $P_{\mathrm{RF}}^\mathrm{T}$ is the transmitted \gls{rf} power, $P_{\mathrm{RF}}^\mathrm{R}$ is the received \gls{rf} power, $P_{\mathrm{DC}}^\mathrm{R}$ is the received \gls{dc} power, and $P_{\mathrm{DC}}^\mathrm{S}$ is the stored \gls{dc} power.
		The power conversion efficiencies are specified below:
		\begin{itemize}
			\item $\eta_1$: Transmitter \gls{dc}-to-\gls{rf} conversion efficiency\footnote{This is different from \gls{pae} used in amplifier rating, which takes into account both \gls{dc} power and input waveform power \cite{Joung2015}.} that depends on the \gls{rf} power amplifier and transmit antenna. It is also called ``drain efficiency'' and state-of-the-art designs can achieve $\eta_1 \ge 70\%$ \cite{Alizadeh2020}.
			\item $\eta_2$: Channel \gls{rf}-to-\gls{rf} conversion efficiency that depends on the wireless environment and \gls{ris} configuration. This is the major bottleneck of \gls{wpt} since the radiated power is inversely proportional to the propagation distance squared.
			\item $\eta_3$: Receiver \gls{rf}-to-\gls{dc} conversion efficiency that depends on the impedance matching and rectifier design. We will discuss its behavior and modelling in the next subsection.
			\item $\eta_4$: Storage \gls{dc}-to-\gls{dc} conversion efficiency that depends on the converter circuit and battery characteristics. Modern power management units can achieve a charging efficiency $\eta_4 \ge 90\%$ \cite{Tan2012}.
		\end{itemize}
		It is worth mentioning that $\eta_1$ and $\eta_3$ also depend on the signal characteristics such as power level, carrier frequency, and \gls{papr} \cite{Clerckx2016a}.
		Extensive efforts have been contributed from \gls{rf}, wireless communications, and power electronic communities to improve the conversion efficiency of individual modules.
		However, it is often overlooked in the literature that a practical \gls{wpt} system is highly \emph{non-linear} since the amplifier and rectifier are very sensitive to the input waveform.
		This non-linear behavior can lead to a {coupling effect} between the modules, such that optimizing $\eta_1$ to $\eta_4$ independently does not necessarily maximize the end-to-end power efficiency $\eta$ \cite{Clerckx2016a}.
		Besides, the system modeling and analysis are subject to practical constraints like diode threshold and reverse-breakdown voltages, device parasitics, impedance mismatch, and harmonic generation  \citep{Valenta2014}.
	\end{subsection}

@@

				\item \emph{Linear region:} When the input power level is relatively low, the output power is proportional to the input and the \gls{rf}-to-\gls{dc} conversion efficiency $\eta_3$ is a constant. Most early \gls{wpt} research (especially from communications society) assume the rectenna works in this region. For a received signal $y(t)$, the harvested \gls{dc} power in this region can be modelled as

@@

				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant and $n_0$ is the truncation order. Selecting $n_0=2$ yields the same result as \eqref{eq:dc_power_linear}, which suggests that the linear model is a special case of the more accurate non-linear model. For a moderate excitation, the contribution of higher-order terms is significant and should be modelled in the harvested \gls{dc} power.

@@

		One of the most important issues in \gls{swipt} is that the energy harvester requires a much higher received signal power (several orders of magnitude) than the information decoder \cite{Clerckx2019}.
		Since the channel \gls{rf}-to-\gls{rf} efficiency $\eta_2$ is the primary constraint on the overall power efficiency, how to combat the pathloss and fading effects has been recognized as a crucial research topic for \gls{wpt} \gls{swipt}.
		Fortunately, this issue can be effectively mitigated by introducing a \gls{ris} to the environment.
		By carefully tuning the scatter response of the \gls{ris} elements, one can potentially achieve the following benefits:
		\begin{itemize}
			\item \emph{Energy focusing:} The scattered waves can be steered towards the receivers or focused on a dedicated ``hotspot zone'' to increase the harvester input power level. This is also helpful to extend the coverage and improve the reliability of the energy link.
			\item \emph{Beam splitting:} Instead of transmitting one strong beam towards each user, the energy signal can be split into multiple weaker beams rerouted by the \gls{ris} to even out the spatial power distribution. This is useful to bypass physical obstacles (especially in high-frequency and large-scale networks) and reduce the health risk of radiation.
		\end{itemize}
		\gls{ris} can also be used to assist the information link by \gls{snr} enhancement and interference suppression, as mentioned in subsection \ref{sc:ris_applications}.
	\end{subsection}

>>>>

		\begin{figure}[H]
			\centering
			\subfloat[Negative-index material\label{fg:nim_focus}]{
				\resizebox{0.45\columnwidth}{!}{
						\input{assets/chapter_2/nim_focus.tex}
				}
			}
			\subfloat[Positive-index material\label{fg:pim_diverge}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/chapter_2/pim_diverge.tex}
				}
			}
			\caption{Refraction through metamaterials. For negative-index material, beams diverging from a point source is set in reverse and converges back to another point behind the material.}
		\end{figure}
		\begin{figure}[H]
			\centering
			\subfloat[Incident wave\label{fg:wave_incident}]{
				\resizebox{!}{4.04cm}{
					\input{assets/chapter_2/wave_incident.tex}
				}
			}
			\subfloat[Reflected wave\label{fg:wave_reflected}]{
				\resizebox{!}{4cm}{
					\input{assets/chapter_2/wave_reflected.tex}
				}
			}
			\caption{Reflection through metamaterials. Yellow dots represent scattering elements. Solid and dashed lines denote wavefronts and rays, respectively. The scattering elements work together to manipulate the phases of incident waves, resulting in a focused beam steered in the intended direction.}
		\end{figure}
		It is worth noticing that refraction and reflection are different forms of {wave scattering} where the signal amplitude and phase are altered by the metamaterial.
		Their contributions can be jointly modeled within the scattering matrix $\mathbf{\Theta}$, which corresponds to the $S$-parameters in microwave engineering and the channel matrix in wireless communications.
		In the next subsection, we will introduce some typical \gls{ris} scattering models and their physical architecture.
	\end{subsection}

	\begin{subsection}{Wave Scattering Models}
		\begin{subsubsection}{Principles}\label{sc:principles}
			\gls{rf} wave can be manipulated by scattering elements made from \emph{programmable metamaterials} or \emph{passive antennas} \cite{Liang2022}.
			As discussed above, the former refracts or reflects the incident signals at the air-cell boundary and mainly applies a phase shift.
			In contrast, the latter allows the wave to feed into the antenna port such that some energy can be absorbed by the circuit and the rest is reradiated to the space.
			An interesting observation is that when excited by an external wave, a scattering element can simultaneously function as an object and a radiator.
			The corresponding scattered field is \cite{Hansen1989}
			\begin{equation}
				\vec{E}_\text{scatter}(Z_\mathrm{L}) = \underbrace{\vec{E}_\text{structural}}_\text{structural component} + \underbrace{\Gamma I_\mathrm{M} \vec{E}_\text{antenna}}_\text{antenna component},
			\end{equation}
			where $Z_\mathrm{L}$ is the load impedance, $\vec{E}_\text{structural}$ is the residual field under perfect matching (i.e., modelling as an object), $\vec{E}_\text{antenna}$ is the radiated field with unit current at the terminal and no external excitation (i.e., modelling as a radiator), $I_\mathrm{M}$ is the current under perfect matching, and $\Gamma$ is the reflection coefficient
			\begin{equation}
				\Gamma = \frac{Z_\mathrm{L} - Z_0^*}{Z_\mathrm{L} + Z_0},
				\label{eq:reflection_coefficient}
			\end{equation}
			and $Z_0$ is the characteristic impedance for programmable metamaterials or the input impedance for passive antennas.
			Specifically,
			\begin{itemize}
				\item \emph{Structural component:} Depends on the geometry and material of the scatterer. It is usually modeled as part of the environment multipath \cite{Thomas2012,Liang2020} or a baseband \gls{dc} offset when the impinging signal is \gls{cw} \cite{Boyer2014}.
				\item \emph{Antenna component:} Depends on the reflection coefficient and load impedance. This is widely exploited for various scattering applications, such as backscatter modulation in \gls{bc} and passive beamforming in \gls{ris} \cite{Zhao2024}.
			\end{itemize}
			We then introduce two canonical \gls{ris} models that will be adopted in the work chapters.
			Advanced models based on field equations (e.g., \cite{Ozdogan2020,Najafi2020}) and parametric fitting (e.g., \cite{Abeywickrama2020}) are also available in the literature for accurate and practical analysis.
			% physics-based (e.g., \cite{Ozdogan2020,Najafi2020}) and practical (e.g., \cite{Abeywickrama2020}) models
		\end{subsubsection}

@@

		\begin{subsubsection}{\glsfmtfull{bd} Model}
			How to model the \gls{ris} response if the passive scattering elements can cooperate with neighbors via physical connections?
			This question has been answered by \cite{Shen2020a} through a \gls{bd} model.
			From a network theory perspective \cite{Ivrlac2010}, a general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable components.
			It allows wave impinging on any element to propagate within the circuit and depart partially from other elements in the same group, such that both amplitude and phase of the scattered wave can be redistributed with zero power loss.
			Fig. \ref{fg:bd_ris_architecture_2} illustrates an 8-element \gls{bd}-\gls{ris} with group size 2 (left) and 4 (right).
			\begin{figure}[H]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\includegraphics{assets/chapter_2/bd_ris_architecture_2.eps}
				}
				\caption{Network model of an 8-element \gls{ris} with group-wise cooperative scattering of group size (a) 2 and (b) 4. The group size is a design parameter to balance the circuit complexity and scattering performance. Source: modified from \cite{Shen2020a}.}
				\label{fg:bd_ris_architecture_2}
			\end{figure}

			% thus redistribute both amplitude and phase of the scattered wave with zero power loss.
			% \begin{figure}[H]
			% 	\centering
			% 	\resizebox{0.75\columnwidth}{!}{
			% 		\includegraphics{assets/chapter_2/bd_ris_architecture_1.eps}
			% 	}
			% 	\caption{Network model of a 4-element \gls{ris} with (a) independent scattering and (b) fully cooperative scattering with all elements interconnected. Source: modified from \cite{Shen2020a}.}
			% 	\label{fg:bd_ris_architecture_1}
			% \end{figure}

			% A general \gls{bd}-\gls{ris} can be modeled as an $N_\mathrm{S}$-port network that divides into $G$ individual groups, each containing $L \triangleq N_\mathrm{S} / G$ elements interconnected by real-time reconfigurable connections.
			Using passive symmetric components (e.g., capacitors and inductors), the scattering matrix of group $g \in \mathcal{G} \triangleq \{1, \ldots, G\}$ is \cite{Shen2020a}
			\begin{equation}
				\mathbf{\Theta}_g = (\jmath \mathbf{X}_g + Z_0 \mathbf{I})^{-1} (\jmath \mathbf{X}_g - Z_0 \mathbf{I}),
			\end{equation}
			which satisfies both \emph{symmetric} and \emph{unitary} properties
			\begin{subequations}
				\begin{equation}
					\mathbf{\Theta}_g = \mathbf{\Theta}_g^\mathsf{T},
					\label{eq:symmetric_property}
				\end{equation}
				\begin{equation}
					\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g = \mathbf{I}.
					\label{eq:unitary_property}
				\end{equation}
			\end{subequations}

			On the other hand, lossless networks may also be built over asymmetric passive components (e.g., ring hybrids and branch-line hybrids) such that the symmetric constraint \eqref{eq:symmetric_property} can be relaxed.
			A 4-port ring hybrid is illustrated in Fig. \ref{fg:ring_hybrid}.
			\begin{figure}[H]
				\centering
				\includegraphics[width=0.5\textwidth]{assets/chapter_2/ring_hybrid.pdf}
				\caption{A 4-port asymmetric ring hybrid. Here the arc length between ports are $\Theta_1 = \Theta_2 = \Theta_3 = \lambda / 4$ and $\Theta_4 = 3 \lambda / 4$ where $\lambda$ is the wavelength. The termination admittances $Y_a$ to $Y_d$ are arbitrary and the characteristic admittances of transmission-line sections are not necessarily the same, such that the scattering parameters can be asymmetric. Source: modified from \cite{Ahn2006}.}
				\label{fg:ring_hybrid}
			\end{figure}

			By reconfiguring passive asymmetric components, we end up with the ultimate passive model where energy conservation \eqref{eq:unitary_property} is the only constraint for each group, as has been widely adopted in quantum physics.
			The overall scattering matrix of asymmetric \gls{bd}-\gls{ris} is thus \emph{block-diagonal with unitary diagonal blocks}
			\begin{equation}
				\mathbf{\Theta} = \mathrm{diag}(\mathbf{\Theta}_1,\ldots,\mathbf{\Theta}_G) =
				\begin{bmatrix}
					\mathbf{\Theta}_1 & \mathbf{0} & \cdots & \mathbf{0} \\
					\mathbf{0} & \mathbf{\Theta}_2 & \cdots & \mathbf{0} \\
					\vdots & \vdots & \ddots & \vdots \\
					\mathbf{0} & \mathbf{0} & \cdots & \mathbf{\Theta}_G
				\end{bmatrix},
				\label{eq:bd_scattering_matrix}
			\end{equation}
			where \eqref{eq:unitary_property} is equivalently denoted as $\mathbf{\Theta}_g \in \mathbb{U}^{L \times L}$.
			The group size $L$ is a design parameter to balance the circuit complexity and scattering performance.
			Diagonal (single-connected) and unitary (fully-connected) \gls{ris} can be viewed as extreme cases with group size $L=1$ and $L=N_\mathrm{S}$, respectively.
			Therefore, the \gls{bd} model \eqref{eq:bd_scattering_matrix} is envisioned to be the next-generation theoretical foundation for passive \gls{ris}, which grants more design freedom and stronger signal processing capability.

			It is also worth mentioning that each group can be abstracted as a mathematical graph with $L$ vertices and a variable number of edges \cite{Nerini2024}.
			Two elements are in the same group if and only if there is at least one path (via edges) between them.
			It implies that instead of connecting every pair of elements, the practical circuit can be designed to have a sparse graph with only a few connections, which is beneficial for reducing the circuit complexity and power loss from non-ideal components.
			Antenna directivity and radiation pattern should also be modeled in the scattering matrix, especially when the locations of users or \gls{ris} are not fixed.
			This has motivated the concept of \gls{star}-\gls{ris} \cite{Mu2021,Liu2021} and multi-sector \gls{ris} \cite{Li2023c} where incident wave is partially steered to various directions for different users.
		\end{subsubsection}
	\end{subsection}
\end{section}

@@

		The block diagram of a closed-loop \gls{ris}-aided \gls{wpt} system is illustrated in Fig. \ref{fg:wpt_architecture}.
		The \gls{rf} signal is generated and radiated by the energy transmitter, propagated through a wireless channel in the presence of a \gls{ris}, captured by the antenna(s) at the receiver, converted to \gls{dc} power by rectifier(s), then passed to the power management unit.
		Upon successful harvesting, the \gls{dc} power is either delivered directly to the device or stored in a battery/super capacitor for future operations.
		When a feedback link is available, one can acquire \gls{csi} at the energy transmitter and exploit it for signal optimization.
		Such a closed-loop \gls{ris}-aided \gls{wpt} system can provide a complete control of transmitter, channel, and receiver, which is essential for maximizing the end-to-end power transfer efficiency
		\begin{equation}
			\eta = \frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{T}} = \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{T}}{P_{\mathrm{DC}}^\mathrm{T}}}_{\eta_1} \underbrace{\frac{P_{\mathrm{RF}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{T}}}_{\eta_2} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{R}}{P_{\mathrm{RF}}^\mathrm{R}}}_{\eta_3} \underbrace{\frac{P_{\mathrm{DC}}^\mathrm{S}}{P_{\mathrm{DC}}^\mathrm{R}}}_{\eta_4},
		\end{equation}
		where $P_{\mathrm{DC}}^\mathrm{T}$ is the transmitted \gls{dc} power, $P_{\mathrm{RF}}^\mathrm{T}$ is the transmitted \gls{rf} power, $P_{\mathrm{RF}}^\mathrm{R}$ is the received \gls{rf} power, $P_{\mathrm{DC}}^\mathrm{R}$ is the received \gls{dc} power, and $P_{\mathrm{DC}}^\mathrm{S}$ is the stored \gls{dc} power.
		The power conversion efficiencies are specified below:
		\begin{itemize}
			\item $\eta_1$: Transmitter \gls{dc}-to-\gls{rf} conversion efficiency\footnote{This is different from \gls{pae} used in amplifier rating, which takes into account both \gls{dc} power and input waveform power \cite{Joung2015}.} that depends on the \gls{rf} power amplifier and transmit antenna. It is also called ``drain efficiency'' and state-of-the-art designs can achieve $\eta_1 \ge 70\%$ \cite{Alizadeh2020}.
			\item $\eta_2$: Channel \gls{rf}-to-\gls{rf} conversion efficiency that depends on the wireless environment and \gls{ris} configuration. This is the major bottleneck of \gls{wpt} since the radiated power is inversely proportional to the propagation distance squared.
			\item $\eta_3$: Receiver \gls{rf}-to-\gls{dc} conversion efficiency that depends on the impedance matching and rectifier design. We will discuss its behavior and modelling in the next subsection.
			\item $\eta_4$: Storage \gls{dc}-to-\gls{dc} conversion efficiency that depends on the converter circuit and battery characteristics. Modern power management units can achieve a charging efficiency $\eta_4 \ge 90\%$ \cite{Tan2012}.
		\end{itemize}
		It is worth mentioning that $\eta_1$ and $\eta_3$ also depend on the signal characteristics such as power level, carrier frequency, and \gls{papr} \cite{Clerckx2016a}.
		Extensive efforts have been contributed from \gls{rf}, wireless communications, and power electronic communities to improve the conversion efficiency of individual modules.
		However, it is often overlooked in the literature that a practical \gls{wpt} system is highly \emph{non-linear} since the amplifier and rectifier are very sensitive to the input waveform.
		This non-linear behavior can lead to a {coupling effect} between the modules, such that optimizing $\eta_1$ to $\eta_4$ independently does not necessarily maximize the end-to-end power efficiency $\eta$ \cite{Clerckx2016a}.
		Besides, the system modeling and analysis are subject to practical constraints like diode threshold and reverse-breakdown voltages, device parasitics, impedance mismatch, and harmonic generation  \citep{Valenta2014}.
	\end{subsection}

@@

				\item \emph{Linear region:} When the input power level is relatively low, the output power is proportional to the input and the \gls{rf}-to-\gls{dc} conversion efficiency $\eta_3$ is a constant. Most early \gls{wpt} research (especially from communications society) assume the rectenna works in this region. For a received signal $y(t)$, the harvested \gls{dc} power in this region can be modeled as

@@

				where $\beta_i = I_\mathrm{S} \frac{R_\mathrm{A}^{i/2}}{i!(n v_\mathrm{T})^i}$ is a constant and $n_0$ is the truncation order. Selecting $n_0=2$ yields the same result as \eqref{eq:dc_power_linear}, which suggests that the linear model is a special case of the more accurate non-linear model. For a moderate excitation, the contribution of higher-order terms is significant and should be modeled in the harvested \gls{dc} power.

@@

		One of the most important issues in \gls{swipt} is that the energy harvester requires a much higher received signal power (several orders of magnitude) than the information decoder \cite{Clerckx2019}.
		Since the channel \gls{rf}-to-\gls{rf} efficiency $\eta_2$ is the primary constraint on the overall power efficiency, how to combat the pathloss and fading effects has been recognized as a crucial research topic for \gls{wpt} and \gls{swipt}.
		Fortunately, this issue can be effectively mitigated by introducing a \gls{ris} to the environment.
		By carefully tuning the scatter response of the \gls{ris} elements, one can potentially achieve the following benefits:
		\begin{itemize}
			\item \emph{Energy focusing:} The scattered waves can be steered towards the receivers or focused on a dedicated ``hotspot zone'' to increase the harvester input power level. This is also helpful to extend the coverage and improve the reliability of the energy link.
			\item \emph{Beam splitting:} Instead of transmitting one strong beam towards each user, the energy signal can be split into multiple weaker beams rerouted by the \gls{ris} to even out the spatial power distribution. This is useful to bypass physical obstacles (especially in high-frequency and large-scale networks) and reduce the health risk of radiation.
		\end{itemize}
		\gls{ris} can also be used to assist the information link by \gls{snr} enhancement and interference suppression, as mentioned in subsection \ref{sc:ris_applications}.
	\end{subsection}
